The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2017-12-05 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Adding single_plot_IRF

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{TFP response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_04}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_13}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real SP500 response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_06}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_14}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real IT investment response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_07}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_15}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real GDP response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_09}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_16}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real Consumption response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_10}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_17}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
